---
title: "Formative Test 1 for HUDK 4050 Core Methods in EDM"
author: "Zhulin Yu"
date: "10/5/2017"
output: html_document
---

Import data to R as data frame D1.

```{r Load Data}
D1 = read.csv("HMXPC13_DI_v2_5-14-14.csv", header = TRUE);
```

5. What does the DI suffix that is appeneded to two of the variable names mean?

DI stands for De-identified. That means personal information is removed usually for privacy protection.

6. Total number of people who received certification in HarvardX/CS50x in 2012: 1287.
```{r Total N of Cert}
n_cert = nrow(subset(D1, certified=="1" & course_id == "HarvardX/CS50x/2012"))
```

7. Total number of people registered for HarvardX/CS50x from Columbia on October 15, 2012:

There is no variable of "register date" or similar in the dataset, so I assume we should use "start_time_DI", though it is not necessarily the register date. Also, no people is from "Columbia" in the raw data, but from "Colombia".

Therefore, I change the question to total number of people registered for HarvardX/CS50x/2012 from Colombia on 2012-10-15, and the number is 10. The code is below.
```{r Total N HarvardX/CS50x from Columbia on 10/15/2012}
n_CS50x_Colmb_10152012d = nrow(subset(D1, registered == 1 & course_id=="HarvardX/CS50x/2012" & final_cc_cname_DI=="Colombia" & start_time_DI == "2012-10-15"))
```

8. I choose Germany:
```{r Data of students from Germany}
D2_all = subset(D1, final_cc_cname_DI=="Germany")
D2 = subset(D2_all, select = c(userid_DI, start_time_DI, final_cc_cname_DI))
```

9. Dateset D1 is too large to run spread on my laptop, so I spread D2 instead.

I add the column "registered" first to D2, then remove duplicates, and finally spread. See the code below.

Final dataset is in data frame D3.

```{r}
library(tidyr)
library(dplyr)
DF = D2_all
D3_tmp = data.frame("user_id" = DF$userid_DI, 
                  "reg_date" = DF$start_time_DI,
                  "registered" = DF$registered)
# remove duplicates in D3_tmp
D3_tmp2 = unique(D3_tmp)

D3 = spread(data=D3_tmp2, reg_date, registered)
```

10. Make row names the student id and then Remove user_id in D3
```{r}
row.names(D3) = D3$user_id
D3 = subset(D3, select = -c(user_id))
```

11. Convert data frame to matrix: M1
```{r}
M1 = data.matrix(D3)
```

12. Transport M1 to M2
```{r}
M2 = t(M1)
```

13. If two students register at the same date, M1 x M2 should give 1, therefore, we can calculate M3 = M1%*%M2.

However, my laptop cannot handle the computation. So I do not run it.
```{r}
#M3 = M1%*%M2
```

14. Convert the diagonal of M3 to NA
```{r}
#diag(M3) =  NA
```